\texttt{Taxonomic supertree construction with}\texttt{\emph{ Incertae sedis}}\texttt{ taxa}

### 2018-04-20 doc/incertae_sedis.tex
Respond to a question.

@@

We seek a semantics for supertrees with \emph{incertae sedis }taxa
that satisfy the following properties:
\begin{enumerate}
    \item An \emph{incertae sedis} node may intrude into its siblings and their
descendants.
    \item Two \emph{incertae sedis} siblings may not be
interdigitated.
    \item Any placement $T\to T^{*}$ of a tree $T$ with
\emph{incertae sedis} taxa is also accessible from a tree $T^{\prime}$
that is created from $T$ by taking a taxon, attaching it to an
ancestor, and marking it \emph{incertae sedis}. \mthcomment{MTH: I don't understand this.}
    \item The semantics of an
\emph{incertae sedis} node does not depend on assigned ranks, but only
on the tree.
    \item Semantics is based on deriving a split for each
branch of the tree.
\end{enumerate}
Here we focus on a split-based
semantics instead of a semantics based on apply of a series of edit
operations to the tree. The split-based semantics allows us to seek
trees that are simultaneously consistent with a set of split-
constraints. The use of a split-based semantics does impose some
limitations. These come primarily because in the edit-based semantics,
after we place an \emph{incertae sedis} taxon, it is no loner
\emph{incertae sedis}, whereas with the split-based semantics taxa are
either always \emph{incertae sedis} or never \emph{incertae sedis}.

>>>>

\newcommand{\bdrcomment}[1]{{\color{blue} #1}\xspace}

@@

We seek a semantics for supertrees with \emph{incertae sedis }taxa
that satisfy the following properties:
\begin{enumerate}
    \item An \emph{incertae sedis} node may intrude into its siblings and their
descendants.
    \item Two \emph{incertae sedis} siblings may not be
interdigitated.
    \item Any placement $T\to T^{*}$ of a tree $T$ with
\emph{incertae sedis} taxa is also accessible from a tree $T^{\prime}$
that is created from $T$ by taking a taxon, attaching it to an
ancestor, and marking it \emph{incertae sedis}. \mthcomment{MTH: I don't understand this.}
\bdrcomment{BDR: Figure \ref{fig:Placing-one-incertae} is an illustration of this.  Suppose you have a genus that is incertae sedis and a family that is incertae sedis and attached at the kingdom level.  We could in theory place the family (.e.g $I$ in the figure) at the right level.  It then sits next to the incertae sedis genus (e.g. $AI$ in the figure).  We could then place the genus within the family.

The goal above is trying to say (and failing to be clear at saying) that if we have a family that is sibling to an incertae sedis genus, then the placement of the genus within the family is still a possibility if we reattach the family as a child of a kingdom node and mark it incertae sedis.
}
    \item The semantics of an
\emph{incertae sedis} node does not depend on assigned ranks, but only
on the tree.
    \item Semantics is based on deriving a split for each
branch of the tree.
\end{enumerate}
Here we focus on a split-based
semantics instead of a semantics based on apply of a series of edit
operations to the tree. The split-based semantics allows us to seek
trees that are simultaneously consistent with a set of split-
constraints. The use of a split-based semantics does impose some
limitations. These come primarily because in the edit-based semantics,
after we place an \emph{incertae sedis} taxon, it is no loner
\emph{incertae sedis}, whereas with the split-based semantics taxa are
either always \emph{incertae sedis} or never \emph{incertae sedis}.
